A Recipe for Scavenging in Vertebrates - the natural history of a behaviour

### 2016-07-12 response_letter.tex

\documentclass{letter}
%\signature{Your name}
%\address{Street \\ City \\ Country}
\begin{document}
\begin{letter}{Company name \\ Street\\ City\\ Country}
\opening{To the editor}

We would like to thank the editor, subject editor and reviewers for their comments. By bringing attention to elements of the manuscript that require more careful communication we believe that you have helped us to significantly improve our manuscript. In this submission we have clarified these areas and added a body of work to bolster the conclusions drawn from our work. Please see below where we consider each of your points in turn.

Reviewer: 3

Comments to the Author
This is a well-written, enjoyable manuscript that assesses the functional traits associated to past and, mostly, current major vertebrate scavengers. As a result, the authors provide a sort of guide to identify the extent of scavenging behaviour among carnivores in both current and past ecosystems. I have several suggestions that should be considered before publication (please see below).

Major comments:

1. Invertebrates are ignored completely throughout the ms. Please specify in the Introduction that this review focuses on vertebrate scavengers. In this line, I recommend to include “in vertebrates” at the end of the title to be more specific. Also, in the “Competition” section you mention competition with vertebrates and micro-organisms, but not with invertebrates. You should consider them in this section (and in “Facilitation”; see next point).

2. I found difficult to follow the main point of the paper because the ms is not well organized. Following a hierarchical order, I’d define four/five main sections: “Introduction”, “The Challenges of Scavenging” (this could be a subsection within the previous section), “Encounter Rate” (with four different subsections: “Metabolism”, “Locomotion”, “Sensory Detection” and “Carcass Availability”), “Handling Time” (which would include “Food Processing”) and “Conclusion”. \\

Moreover, “Competition” and “Facilitation” (I strongly encourage you to consider not only competitive, but also facilitative processes, which are mostly neglected in your review) should be treated as transversal factors that can modulate each of the abovementioned parameters. Thus, I’d include them in a different section, or mention the competitive and facilitative processes related to each parameter within each subsection. Fig. 1 should be re-organized accordingly.

3. The use of the scientific literature on scavenging is deficient, especially for a review paper like this. A number of key references are missing, e.g., Selva \& Fortuna (2007 Proc. R Soc. B 274:1101-1108), Wilson \& Wolkovich (2011 TREE 23:129-135), Beasley et al. (2012 Oikos 121:1021-1026), Cortés-Avizanda et al. (2012 Ecology 93:2570-2579), Cortés-Avizanda et al. (2014 Ecology 95:1799-1808), Moleón et al. (2014 Biol. Rev. 89:1042-1054), Pereira et al. (2014 Mammal Rev. 44:44-55), Périquet et al. (2015 Biol. Rev. 90:1197-1214), Mateo-Tomás et al. (2015 Divers. Distrib. 21:913-924), Moleón \& Sánchez-Zapata (2015 BioScience 65:1003-1010), Moreno-Opo et al. (2016 Behav. Ecol.), Sebastián-González et al. (2016 Ecology 97:95-105). Your literature synthesis might benefit from the reading of these articles, for instance regarding competitive and facilitative interactions among scavengers. Also, the review would be more informative and useful for readers. Next I mention some particular comments regarding the use of the references (I mention others in Minor comments): \\

Page 2, 1st sentence: but see Moleón \& Sánchez-Zapata (2015); many of the most charismatic vertebrates of the world are scavengers. Rather than “scavengers”, what is not charismatic is probably “scavenging”.

We now refer to the behaviour rather than the species as lacking charisma.

 Page 2, 13th line: Moleón \& Sánchez-Zapata (2015) may be more appropriate than Koenig (2006) because the former is more general and not restricted to vultures.
 Page 2, lines 17th-18th: see Pereira et al. (2014) and Périquet et al. (2015) for reviews.

These references have been added.

 Page 3, bottom paragraph, bottom line: this is not true, as scavenging may indirectly affect herbivore populations and thus carrion availability (see Moleón et al. 2014 Biol. Rev.).

The potential for scavengers to affect carrion availability has been acknowledged.

 Page 5, bottom paragraph, 1st sentence: Mateo-Tomás et al. (2015) is more general than Kendall (2013).
 Page 8, 1st and 2nd sentences: see Pereira et al. (2014) and Périquet et al. (2015).
 Page 8, 3rd sentence: you may also cite DeVault et al. (2003) and Pereira et al. (2014).

These references have been added.

 Page 8, 8th-17th lines: please reword; wild dogs hardly scavenge, while leopards and lions are frequent scavengers (see Pereira et al. 2014).

We have reworded this section to make the more general point that ambush predators can rely more on hunting than can cursorial species, a point explicitly stated in the Pereira et al. (2014) article, which we now cite.

 Page 11, 1st sentence: see Kane et al. (2014) and Moleón et al. (2014 Biol. Rev.) for inter-specific interactions.
 Page 11, 4th sentence: Kane et al. (2014) is not appropriate here because it is about inter-specific interactions; use Cortés-Avizanda et al. (2014) instead.
 Page 14, 2nd paragraph, 1st sentence: see also Moleón et al. (2014 Biol. Rev.) and Pereira et al. (2014).
 Page 14, 2nd paragraph, 2nd sentence: see better Pereira et al. (2014) and Périquet et al. (2015). 
 Page 14, bottom paragraph, 3rd sentence: you may also consider Moreno-Opo et al. (2016).
 Page 15, 2nd paragraph, 2nd sentence: see also Moleón et al. (2014 Biol. Rev.) and Pereira et al. (2014).

All of these references have been added.

4. You should include more discussion about the importance of carcass size throughout the ms, as it has a strong influence on scavenging patterns and interactions among vertebrates and between vertebrates and smaller carrion consumers (e.g., see Moleón et al. 2015).

Minor comments:

GENERAL

1. Please provide line numbers to facilitate the reviewing process.

Line numbers have now been included.

ABSTRACT

2. You could remove “, the first to our knowledge”.

This has been removed.

3. Also, you could mention some relevant specific findings of your synthesis.

THE CHALLENGES OF SCAVENGING

4. Page 3, 1st sentence: “often difficult to predict” compared to what? Please specify. There are many examples in which carrion is highly predictable, e.g., during salmon spawning (see also Pereira et al. 2014).

ENCOUNTER RATE

5. Page 3, bottom paragraph, 3rd line: change “Alternatively” to “Also”?

This has been changed.

METABOLISM

6. Page 4, 1st sentence: “the sporadic nature of carrion”; please explain.

LOCOMOTION

7. Page 4, bottom paragraph, 1st sentence: change “inherent” to “relative”.

This has been changed.

8. Page 4, bottom paragraph, 3rd sentence: remove “, paradoxically,”.

This has been deleted.

9. Page 5, 2nd paragraph, 1st sentence: change “appear” to “appeared”. Also, specify Mya for the Cretaceous period.

This has been changed.

10. Page 9, top paragraph: please be more cautious in your assertion, as cooperation skills and tools of early hominins probably allowed them to defend and usurp carcasses from more powerful scavengers.

We have changed this paragraph and take into account the authors' reference to tool use and sociality in hominins. The point is that even with these advantages, running to a carcass over long distances still wasn't energetically sensible.

DETECTION

11. Page 11, top and 2nd paragraph, 1st sentence: this is about facilitation. As said above, facilitative processes may affect other parameters as well, not only the ability to detect carrion.

12. Page 11, last sentence: explain why wind speed affects the olfactory capacity of an aquatic species.

PREY AVAILABILITY

13. I’d change this title to “Carcass Availability”, which is more specific.

This has been changed.

14. Among the different components of carcass availability, e.g., abundance, duration, predictability and accessibility, in this section you only talk about abundance and duration. You should also discuss about carcass predictability (e.g., see Cortés-Avizanda et al. 2012) and carcass accessibility (e.g., see DeVault \& Krochmal 2002).

15. Page 12, 2nd paragraph, 1st sentence: as said before, this is not true, given that scavenging may indirectly affect herbivore populations and thus carrion availability (see Moleón et al. 2014 Biol. Rev.).

We have removed the part of the sentence where we mistakenly suggest that scavengers cannot affect carrion availability.

16. Page 13, 3rd and 4th sentences: whaling has exerted also a huge negative impact on scavengers by depleting whale populations. If you are going to talk about human impacts, maybe is better to do it at the end of the ms, perhaps in a new section in which you explore which scavenging traits could be more successful in a human dominated world.

This has been removed.

17. You should also take into account facilitative processes. For instance, some scavengers are able to access the interior of carcasses only once other, more powerful species, has opened the skin (see Moleón et al. 2014 Biol. Rev.).

18. Page 14, bottom paragraph, 2nd sentence: I’d change it to “This is true for many vultures and other major avian scavengers such as albatrosses who all have […]”.

We have reworded the sentence as suggested.

FOOD PROCESSING

19. Page 16, 2nd paragraph, 6th sentence: insert “Within mammals,” before “This ability”.

This has been added.

20. Page 17, 2nd paragraph, 4th sentence: do you refer to species or individuals? Higher species diversity doesn’t mean more individuals.

The reference of Pobiner (2015) states that there were more individuals and we have changed the sentence to reflect this.

21. Page 18, 1st sentence: change “enabling” to “enable”.

This has been changed.

22. Page 18, 3rd sentence: “thus”? I don’t understand this sentence; could you please reword it?

We have reworded this sentence. The idea is that early birds didn't have beaks and so could more easily eat meat. This is in contrast to modern birds where a beak may be a hindrance.

23. Page 18, 5th sentence: “The mix of strong and weak features in their skull morphology”; please explain it.

CONCLUSION

24. Page 18, bottom paragraph, 3rd sentence: change “technique” to “approach”?

This has been changed.

FIGURES

25. Fig. 2: you may insert the name and Mya range of each period in the X axis rather than in the figure legend. Also, I’d indicate “aerial”, “terrestrial” and “aquatic” in the Y axis rather than in the legend.

Hope this helps,
Marcos Moleón

\bigskip
Yours Sincerely,

Adam Kane and co-authors 
%\closing{Yours Faithfully,}
%\ps{P.S. Here goes your ps.}
%\encl{Enclosures.}
\end{letter}
\end{document}

### 2016-07-12 natural history of scavenging.tex
start of response

\title{A Recipe for Scavenging - the natural history of a behaviour}
%TG: nice title! I'd replace the hyphen with a comma though
\running{Scavenging in vertebrates}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging, the first to our knowledge. 
Our idea of a scale of scavenging can be applied to any species at any time to judge the importance of this behaviour in its diet. 
\end{abstract}

@@

\section*{Introduction}

Historically, scavengers have not been viewed as the most charismatic of animals.
This may go some way to explaining the gap in our knowledge of the prevalence of this behaviour \citep{devault2003scavenging}.
Professor Sanborn Tenney writing in 1877 for The American Naturalist had this to say about one well known group, ``prominent among the mammalian scavengers are the hyenas, the ugliest in their general appearance of all the flesh eaters."
He contrasts these with ``nobler kinds" of carnivores such as lions and tigers \citep{tenney1877few}.
Even aside from our own subjective biases, scavenging is a difficult behaviour to detect after the fact.
Without catching a carnivore in the act of killing we are left to infer how the prey was killed.
Some simple heuristics can inform us, for instance, in cases where the prey item was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.
But clearly, a scavenger does not only feed on animals too big for it to have hunted.
The obvious lack of direct behavioural data compounds the difficulty of discerning scavenging from predation among extinct forms.
Indeed, a single species of dinosaur notwithstanding \citep{carbone2011intra}, a synthesis describing the natural history of scavengers is absent from the literature.
With research on scavenging on the rise \citep{manga2006vulture} we are now beginning to realise the extent of this behaviour such that, ``in some ecosystems, vertebrates have been documented to assimilate as much as 90\% of the available carrion" \citep{beasley2015vertebrates}.
This has profound implications for the trophic ecology of these systems and particularly our models of them.
Even Tenney’s noble big cats are now known to take in a significant portion of carrion in their diet where some lion populations acquire over 50\% of their meat from carcasses \citep{jones2015african}.
While recognising the difficulty in directly observing scavenging, it is possible to turn to other methods in order to discern the most suitable morphologies, physiologies and environments for a scavenging lifestyle to prosper.
Here we chart the natural history of scavenging by assessing the potential for the behaviour in dominant vertebrate groups given their ecology and functional traits.
%It is our aim in this review to employ these methods to gain an understanding of scavengers past and present.

%the intro needs to lead towards a aim a bit more strongly

\subsection*{The Challenges of Scavenging} 
The chief hurdle to scavenging is finding a resource that is often difficult to predict in space and time.
Through chance alone many species will avail of some opportunistic scavenging. 
However, species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins  \citep{ruxton2014fruit}. 
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics but are outside the selection pressures on the scavenger.
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place any vertebrate species, past or present, and assess the likely importance of carrion in its diet.

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. The black and white gradient bar on the top represent the proportion of scavenging in the diet, ranging from low (- -) on the left hand side to high (+ +) on the right hand side. Blue lines indicate that a reduction in the factor will lead to more or less proportion of scavenging in the diet and red lines indicate an increase.}
%Silhouettes from left to right on each line: \textit{Somelizard ofsomesort}, \textit{Felis silvestris}, \textit{Somelizard ofsomesort}, Diomedeidae, \textit{Antennarius striatus}, \textit{Gyps}, Actinopterigii skeleton, \textit{Stegosaurus} skeleton, \textit{Gyps}, \textit{Crocuta crocuta}, \textit{Rousettus aegyptiacus}, \textit{Crocuta crocuta}.
\label{Summary_figure}
\end{figure}

%KH: need paragraph for how do we know something is (was) a scavenger
\section*{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus  expect selection pressures to act on the various traits that govern these parameters.
Alternatively, selection might drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species ability to  process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced,  an aspect which the selective forces acting on the scavenger have no influence.

%As such, scavenging potential is strongly affected by search rates, which are determined by anatomy, physiology and behaviour which are all under selective pressure, as well as the type of environment the scavenger is foraging in.

\subsection*{Metabolism}
Because of the sporadic nature of carrion we would expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found that sharks, as ectothermics, have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time \ref{handlingTime}). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

\subsection*{Locomotion}
The inherent unpredictability of carrion also means scavenging depends more on the ability to efficiently move over larger areas than does predation.
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is, paradoxically, found in flying species. 
Despite the energetic costs of flight, the only known vertebrate obligate scavengers are the old and the new world vultures. 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only twice their metabolic rate \citep{hedenstrom1993migration,spivey2014analysing}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

The groups from which these modern soaring birds arose, appear during the Palaeocene \citep[66 - 56 Million years ago (Mya); ][]{Jetz2012, Jarvis2014} and Cretaceous \citep{chiappe2006early} respectively. 
However, soaring flight is likely to be far older than this with avian flight originating in the Late Jurassic (163.5 - 145 Mya) and vertebrate flight in the Late Triassic (235 - 201.3 Mya) coincident with the pterosaurs. 
Indeed, scavenging among pterosaurs has been hypothesised many times before \citep{witton2008reappraisal}. 
Certain groups of these animals could reach enormous sizes \citep[e.g. Azhdarchids with wingspans of 11 metres; ][]{witton2010size} and, notably, appear to have engaged in soaring flight \citep{witton2010size}.
It seems probable that at least some of these extinct species used soaring as a means for scavenging \citep{witton2013pterosaurs}. 
%KH added "at least some of these" as it was not clear what species used soaring as a means for scavenging.
While soaring is perhaps the only viable means of locomotion that allows for an obligate, scavenging life-style \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

We know that many extant birds exist as facultative scavengers because storks, raptors and corvids all take substantial quantities of carrion in their diet \citep{kendall2013alternative}. 
Similarly we would expect that extinct species would also scavenge in a similar fashion depending on the efficiency of their flight. 
For example, early birds such as \textit{Archaeopteryx} are predicted to have been poor, relatively inefficient fliers \citep{nudds2010narrow} and so ill-suited to finding carrion. 
The importance of efficient flying over large areas may explain the lack of scavenging behaviour in bats as they are generally nocturnal, a time when they would receive no aid from convective air currents \citep{norberg2012vertebrate}.

@@

Interestingly, however, style of swimming in fishes does not significantly affect the cost of movement \citep{williams1999evolution}, hence it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.
%KH I moved this down here as it kinda throws our shark soaring thing out the window (which I like as a linking function). However I think this kinda solves our problems in the complexity of swimming by saying apart from large ranges ability to eat is probably more important.

We might expect then that by combining an aquatic environment and an endothermic metabolism marine mammals would especially prosper as scavengers. %, especially as this group has perhaps the largest home range of any animals (whales and shit).
Fossil pinnipeds and cetaceans from 60 Mya have transitional features indicative of their evolutionary trajectory to fully aquatic species \citep{williams1999evolution}.  
But despite their movement away from land their energetic savings were negligible because the \textit{total} cost incurred by a swimming marine mammal is high \citep{williams1999evolution}. 
Indeed, the total energetic cost is similar to an equivalent terrestrial or aerial mammal \citep{williams1999evolution}.
This underscores the trade offs between the benefits of endothermy in terms of activity periods and the costs of maintaining such an energetically expensive system. 
That said, aquatic endotherms have and do scavenge. 
For instance, early whales such as \textit{Basilosaurus} (38 - 36.5 Mya) seem to have fit into the same niche as killer whales (\textit{Orcinus orca}) and we have some evidence for scavenging in both \citep{fahlke2012bite,Whitehead415}.

%%KH Is there anything we should add about other extinct groups such as plesiosaurs and https://en.wikipedia.org/wiki/Plesiosauria#Gait maybe an air breathing non-airbreathing devide would be good.

%% AK:  Need to be careful here because this whole idea of sprawling posture being worse off than erect posture is not that well supported in the literature. 
%% Great Transformations in Vertebrate Evolution By Kenneth P. Dial, Neil Shubin, Elizabeth L. Brainerd talks about it at length 
%% So I think this should stay pitched as an endo/ ectothermy thing rather than posture 
Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments support must be provided through the animal's posture. % leading to trade offs between low cost of maintain and the efficiency of transport. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo coastal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.

% For example, the sprawling posture of many ectotherm groups (except frogs!) would be expected to allow for a lower maintenance cost relating to body support in comparison to groups with the limbs position underneath the body, such as mammals, aves and dinosaurs.
%KH: I agree with TG and have removed the gas exchange thing as its a physiology thing only applicable to certain groups and not got to do with terrestrial environments really. I also removed the 
%Also that reference is from 1975, is this up to date?

>>>>

\title{A Recipe for Scavenging in Vertebrates - the natural history of a behaviour}

\running{Scavenging in vertebrates}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
Our idea of a scale of scavenging can be applied to any species at any time to help judge the importance of this behaviour in its diet. 
\end{abstract}

@@

\section{Introduction}

Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and detailing its ecological consequences across modern ecosystems where we are beginning to appreciate the implications for the trophic ecology of these systems \citep{pereira2014facultative,periquet2015lion}.
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient \citep{pereira2014facultative}.
Unfortunately, the lack of direct behavioural data makes it difficult to discern scavenging from predation among extinct forms where it was surely exhibited to a similar extent among prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.
But clearly, a scavenger does not only feed on animals too big for it to have hunted.
There are other methods however, that allow us to discern the most suitable morphologies, physiologies and environments for a scavenging lifestyle to prosper e.g. energetics models, comparative anatomy, palaeontology etc. \citep{shipman1986scavenging,ruxton2003could}. 
Yet, a synthesis describing the natural history of scavengers is absent from the literature.
Here we rectify this shortcoming in charting the natural history of scavenging by assessing its potential among extinct vertebrate groups given their ecology, functional traits and the enviornmental context.

\subsection{The Challenges of Scavenging}

Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}. 
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place an extinct vertebrate carnivore and assess the likely importance of carrion in its diet.

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. The black and white gradient bar on the top represent the proportion of scavenging in the diet, ranging from low (- -) on the left hand side to high (+ +) on the right hand side. Blue lines indicate that a reduction in the factor will lead to more or less proportion of scavenging in the diet and red lines indicate an increase.}
\label{Summary_figure}
\end{figure}

\section{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus expect selection pressures to act on the various traits that govern these parameters.
Selection might also drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species ability to process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced. 
Scavengers can drive this process indirectly, for instance, by consuming the majority of carrion, obligate scavengers deny a resource to their facultative counterparts obliging the latter to hunt more and thus produce more carrion \citep{moleon2014inter}.

\subsection{Metabolism}
Because of the sporadic nature of carrion we would expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found that sharks, as ectothermics, have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time \ref{handlingTime}). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

\subsection{Locomotion}
The relative unpredictability of carrion also means scavenging depends more on the ability to efficiently move over larger areas than does predation.
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is found in flying species. 
Despite the energetic costs of flight, the only known vertebrate obligate scavengers are the old and the new world vultures. 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only twice their metabolic rate \citep{hedenstrom1993migration,spivey2014analysing}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

The groups from which these modern soaring birds arose, appeared during the Palaeocene \citep[66 - 56 Million years ago (Mya); ][]{Jetz2012, Jarvis2014} and Cretaceous \citep[145.5 - 65.5 Mya; ][]{chiappe2006early} respectively. 
However, soaring flight is likely to be far older than this with avian flight originating in the Late Jurassic (163.5 - 145 Mya) and vertebrate flight in the Late Triassic (235 - 201.3 Mya) coincident with the pterosaurs. 
Indeed, scavenging among pterosaurs has been hypothesised many times before \citep{witton2008reappraisal}. 
Certain groups of these animals could reach enormous sizes \citep[e.g. Azhdarchids with wingspans of 11 metres; ][]{witton2010size} and, notably, appear to have engaged in soaring flight \citep{witton2010size}.
It seems probable that at least some of these extinct species used soaring as a means for scavenging \citep{witton2013pterosaurs}.

While soaring is perhaps the only viable means of locomotion that allows for an obligate, scavenging life-style \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

We know that many extant birds exist as facultative scavengers because storks, raptors and corvids all take substantial quantities of carrion in their diet \citep{mateo2015regional}. 
Similarly we would expect that extinct species would also scavenge in a similar fashion depending on the efficiency of their flight. 
For example, early birds such as \textit{Archaeopteryx} are predicted to have been poor, relatively inefficient fliers \citep{nudds2010narrow} and so ill-suited to finding carrion. 
The importance of efficient flying over large areas may explain the lack of scavenging behaviour in bats as they are generally nocturnal, a time when they would receive no aid from convective air currents \citep{norberg2012vertebrate}.

@@

Interestingly, however, style of swimming in fishes does not significantly affect the cost of movement \citep{williams1999evolution}, hence it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.

We might expect then that by combining an aquatic environment and an endothermic metabolism marine mammals would especially prosper as scavengers. 
Fossil pinnipeds and cetaceans from 60 Mya have transitional features indicative of their evolutionary trajectory to fully aquatic species \citep{williams1999evolution}.  
But despite their movement away from land their energetic savings were negligible because the \textit{total} cost incurred by a swimming marine mammal is high \citep{williams1999evolution}. 
Indeed, the total energetic cost is similar to an equivalent terrestrial or aerial mammal \citep{williams1999evolution}.
This underscores the trade offs between the benefits of endothermy in terms of activity periods and the costs of maintaining such an energetically expensive system. 
That said, aquatic endotherms have and do scavenge. 
For instance, early whales such as \textit{Basilosaurus} (38 - 36.5 Mya) seem to have fit into the same niche as killer whales (\textit{Orcinus orca}) and we have some evidence for scavenging in both \citep{fahlke2012bite,Whitehead415}.

Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments support must be provided through the animal's posture. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo coastal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.
